Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-04-10 paper.tex
updated table 08-08 due to paranoia
Tried to clear up what we mean by "optimal" in 08-08
Redraw schedule figure

\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathtools}
\usepackage[rightcaption]{sidecap}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{framed}
\usepackage{tikz}

@@

\begin{figure}[tb]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{schedule.pdf}
\caption{A pictorial representation of the entire model of the schedule for 7 skippers and 6 boats.
The schedule is reproduced top right. On the right we have the 7 skippers, on top left the
$\modMatch$ array, at the bottom $\timeVar$ and middle left the $\match$ array. The yellow arrows
signify channeling between parts of the model.}
\label{schedChanges}
\end{figure}

>>>>

\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathtools}
\usepackage[rightcaption]{sidecap}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{framed}
\usepackage{tikz}
\usepackage{pdflscape}
\usepackage{afterpage}

@@

\afterpage{\clearpage\begin{landscape}
\begin{figure}[p]
    \centering
    \begin{tikzpicture}
        \begin{scope}
            \node (Time) at (-2, 0) { $\timeVar$ };
            \node (Time0) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (0, 0) {
                \nodepart[text width=1.5em, align=center] {one}   (0,1)
                \nodepart[text width=1.5em, align=center] {two}   (2,3)
                \nodepart[text width=1.5em, align=center] {three} (4,5)
            };
            \node (Time1) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (2.2, 0) {
                \nodepart[text width=1.5em, align=center] {one}   (0,2)
                \nodepart[text width=1.5em, align=center] {two}   (4,6)
                \nodepart[text width=1.5em, align=center] {three} (1,5)
            };
            \node (Time2) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (4.4, 0) {
                \nodepart[text width=1.5em, align=center] {one}   (2,6)
                \nodepart[text width=1.5em, align=center] {two}   (0,5)
                \nodepart[text width=1.5em, align=center] {three} (1,3)
            };
            \node (Time3) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (6.6, 0) {
                \nodepart[text width=1.5em, align=center] {one}   (5,6)
                \nodepart[text width=1.5em, align=center] {two}   (0,3)
                \nodepart[text width=1.5em, align=center] {three} (1,4)
            };
            \node (Time4) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (8.8, 0) {
                \nodepart[text width=1.5em, align=center] {one}   (3,5)
                \nodepart[text width=1.5em, align=center] {two}   (1,6)
                \nodepart[text width=1.5em, align=center] {three} (2,4)
            };
            \node (Time5) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (11.0, 0) {
                \nodepart[text width=1.5em, align=center] {one}   (3,6)
                \nodepart[text width=1.5em, align=center] {two}   (0,4)
                \nodepart[text width=1.5em, align=center] {three} (2,5)
            };
            \node (Time6) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (13.2, 0) {
                \nodepart[text width=1.5em, align=center] {one}   (3,4)
                \nodepart[text width=1.5em, align=center] {two}   (1,2)
                \nodepart[text width=1.5em, align=center] {three} (0,6)
            };
        \end{scope}

        \begin{scope}[yshift=5cm, xshift=-3.5cm]
            \node [anchor=north west] (MatchTable) at (0, 0) {
                \begin{minipage}{4.5cm}
                    \centering
                    \setlength{\aboverulesep}{0pt}
                    \setlength{\belowrulesep}{0pt}
                    \setlength{\extrarowheight}{.75ex}
                    \setlength{\tabcolsep}{2pt}
                    \begin{tabular}{cccccccc}
                        & 0 & 1 & 2 & 3 & 4 & 5 & 6 \\ \cmidrule{2-8}
                        \multicolumn{1}{l@{\hspace{1em}}|}{0} & ~-~ & 0 & 3 & 10 & 16 & 7 & 20 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{1} & & ~-~ & 19 & 8 & 11 & 5 & 13 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{2} & & & ~-~ & 1 & 14 & 17 & 6 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{3} & & & & ~-~ & 18 & 12 & 15 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{4} & & & & & ~-~ & 2 & 4 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{5} & & & & & & ~-~ & 9 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{6} & & & & & & & ~-~ \\
                    \end{tabular}
                \end{minipage}
            };
            \node [above=-0.1 of MatchTable.north west, anchor=south west] (Match) { $\match$ };
        \end{scope}

        \begin{scope}[yshift=9.9cm, xshift=-3.5cm]
            \node [anchor=north west] (ModMatchTable) at (0, 0) {
                \begin{minipage}{4.5cm}
                    \centering
                    \setlength{\tabcolsep}{2pt}
                    \setlength{\aboverulesep}{0pt}
                    \setlength{\belowrulesep}{0pt}
                    \setlength{\extrarowheight}{.75ex}
                    \begin{tabular}{cccccccc}
                        & 0 & 1 & 2 & 3 & 4 & 5 & 6 \\ \cmidrule{2-8}
                        \multicolumn{1}{l@{\hspace{1em}}|}{0} & ~-~ & 0 & 1 & 3 & 5 & 2 & 6 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{1} & 0 & ~-~ & 6 & 2 & 3 & 1 & 4 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{2} & 1 & 6 & ~-~ & 0 & 4 & 5 & 2 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{3} & 3 & 2 & 0 & ~-~ & 6 & 4 & 5 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{4} & 5 & 3 & 4 & 6 & ~-~ & 0 & 1 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{5} & 2 & 1 & 5 & 4 & 0 & ~-~ & 3 \\
                        \multicolumn{1}{l@{\hspace{1em}}|}{6} & 6 & 4 & 2 & 5 & 1 & 3 & ~-~ \\
                    \end{tabular}
                \end{minipage}
            };
            \node [above=-0.1 of ModMatchTable.north west, anchor=south west] (ModMatch) { $\modMatch$ };
        \end{scope}

        \begin{scope}[yshift=10.2cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
            \node at (-5, 0) { $\mathit{Skipper~0}$ };

            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
            rectangle split part fill={uofgcobalt,uofgcobalt,uofgsunshine,uofgsunshine,uofgthistle,uofgsunshine,uofglawn}] at (0, 0) {
                \nodepart[text width=2em, align=center] {one}   \textsc{F}
                \nodepart[text width=2em, align=center] {two}   \textsc{F}
                \nodepart[text width=2em, align=center] {three} \textsc{M}
                \nodepart[text width=2em, align=center] {four}  \textsc{M}
                \nodepart[text width=2em, align=center, text=white] {five} \textsc{B}
                \nodepart[text width=2em, align=center] {six}   \textsc{M}
                \nodepart[text width=2em, align=center] {seven} \textsc{L}
            };

            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
                \nodepart[text width=0.75em, align=center] {one} 1
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
                \nodepart[text width=0.75em, align=center] {one} 2
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 5
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 3
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 4
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 6
            };

        \begin{scope}[yshift=8.8cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
            \node at (-5, 0) { $\mathit{Skipper~1}$ };

            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
            rectangle split part fill={uofgcobalt,uofglawn,uofglawn,uofglawn,uofgsunshine,uofgthistle,uofgsunshine}] at (0, 0) {
                \nodepart[text width=2em, align=center] {one}   \textsc{F}
                \nodepart[text width=2em, align=center] {two}   \textsc{L}
                \nodepart[text width=2em, align=center] {three} \textsc{L}
                \nodepart[text width=2em, align=center] {four}  \textsc{L}
                \nodepart[text width=2em, align=center] {five}  \textsc{M}
                \nodepart[text width=2em, align=center, text=white] {six}   \textsc{B}
                \nodepart[text width=2em, align=center] {seven} \textsc{M}
            };

            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
                \nodepart[text width=0.75em, align=center] {one} 0
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 5
            };

            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 3
            };

            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 4
            };

            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 6
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 2
                \nodepart[text width=0.75em, align=center] {three}
            };

        \begin{scope}[yshift=7.4cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
            \node at (-5, 0) { $\mathit{Skipper~2}$ };

            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
            rectangle split part fill={uofgsunshine,uofgcobalt,uofgcobalt,uofgthistle,uofglawn,uofglawn,uofgsunshine}] at (0, 0) {
                \nodepart[text width=2em, align=center] {one}   \textsc{M}
                \nodepart[text width=2em, align=center] {two}   \textsc{F}
                \nodepart[text width=2em, align=center] {three} \textsc{F}
                \nodepart[text width=2em, align=center, text=white] {four}  \textsc{B}
                \nodepart[text width=2em, align=center] {five}  \textsc{L}
                \nodepart[text width=2em, align=center] {six}   \textsc{L}
                \nodepart[text width=2em, align=center] {seven} \textsc{M}
            };

            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 3
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
                \nodepart[text width=0.75em, align=center] {one} 0
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
                \nodepart[text width=0.75em, align=center] {one} 6
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 4
            };

            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 5
            };

            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 1
                \nodepart[text width=0.75em, align=center] {three}
            };

        \begin{scope}[yshift=6.0cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
            \node at (-5, 0) { $\mathit{Skipper~3}$ };

            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
            rectangle split part fill={uofgsunshine,uofgthistle,uofglawn,uofgsunshine,uofgcobalt,uofgcobalt,uofgcobalt}] at (0, 0) {
                \nodepart[text width=2em, align=center] {one}   \textsc{M}
                \nodepart[text width=2em, align=center, text=white] {two}   \textsc{B}
                \nodepart[text width=2em, align=center] {three} \textsc{L}
                \nodepart[text width=2em, align=center] {four}  \textsc{M}
                \nodepart[text width=2em, align=center] {five}  \textsc{F}
                \nodepart[text width=2em, align=center] {six}   \textsc{F}
                \nodepart[text width=2em, align=center] {seven} \textsc{F}
            };

            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 2
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 1
            };

            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 0
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
                \nodepart[text width=0.75em, align=center] {one} 5
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
                \nodepart[text width=0.75em, align=center] {one} 6
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
                \nodepart[text width=0.75em, align=center] {one} 4
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

        \begin{scope}[yshift=4.6cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
            \node at (-5, 0) { $\mathit{Skipper~4}$ };

            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
            rectangle split part fill={uofglawn,uofgsunshine,uofgthistle,uofglawn,uofglawn,uofgsunshine,uofgcobalt}] at (0, 0) {
                \nodepart[text width=2em, align=center] {one}   \textsc{L}
                \nodepart[text width=2em, align=center] {two}   \textsc{M}
                \nodepart[text width=2em, align=center, text=white] {three} \textsc{B}
                \nodepart[text width=2em, align=center] {four}  \textsc{L}
                \nodepart[text width=2em, align=center] {five}  \textsc{L}
                \nodepart[text width=2em, align=center] {six}   \textsc{M}
                \nodepart[text width=2em, align=center] {seven} \textsc{F}
            };

            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 5
            };

            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 6
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 1
            };

            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 2
            };

            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 0
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
                \nodepart[text width=0.75em, align=center] {one} 3
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

        \begin{scope}[yshift=3.2cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
            \node at (-5, 0) { $\mathit{Skipper~5}$ };

        \begin{scope}[yshift=1.8cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
            \node at (-5, 0) { $\mathit{Skipper~6}$ };

            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
            rectangle split part fill={uofgthistle,uofgsunshine,uofgcobalt,uofgcobalt,uofgsunshine,uofgcobalt,uofglawn}] at (0, 0) {
                \nodepart[text width=2em, align=center, text=white] {one}   \textsc{B}
                \nodepart[text width=2em, align=center] {two}   \textsc{M}
                \nodepart[text width=2em, align=center] {three} \textsc{F}
                \nodepart[text width=2em, align=center] {four}  \textsc{F}
                \nodepart[text width=2em, align=center] {five}  \textsc{M}
                \nodepart[text width=2em, align=center] {six}   \textsc{F}
                \nodepart[text width=2em, align=center] {seven} \textsc{L}
            };

            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 4
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
                \nodepart[text width=0.75em, align=center] {one} 2
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
                \nodepart[text width=0.75em, align=center] {one} 5
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two} 1
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
                \nodepart[text width=0.75em, align=center] {one} 3
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three}
            };

            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
                \nodepart[text width=0.75em, align=center] {one}
                \nodepart[text width=0.75em, align=center] {two}
                \nodepart[text width=0.75em, align=center] {three} 0
            };

        \begin{scope}
            \node [anchor=north west] (Schedule) at (10.5, 8) {
                \begin{minipage}{4.5cm}
                    \centering
                    \setlength{\tabcolsep}{3pt}
                    \begin{tabular}{cccc}
                        \toprule
                        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
                        0 & (0,1) & (2,3) & (4,5) \\
                        1 & (0,2) & (4,6) & (1,5) \\
                        2 & (2,6) & (0,5) & (1,3) \\
                        3 & (5,6) & (0,3) & (1,4) \\
                        4 & (3,5) & (1,6) & (2,4) \\
                        5 & (3,6) & (0,4) & (2,5) \\
                        6 & (3,4) & (1,2) & (0,6) \\ \bottomrule
                    \end{tabular}
                \end{minipage}
            };
            \node [above=0 of Schedule.north west, anchor=south west] (Match) { \hspace*{1em}$\mathit{schedule}$ };
        \end{scope}

        \begin{scope}
            \draw [<->, thick, >=latex] (-0.5, 5.1) to (-0.5, 5.7);
            \draw [<->, thick, >=latex] (-0.5, 0.4) to (-0.5, 1.0);
            \draw [<->, thick, >=latex] (1.6, 2.6) to (2.3, 2.6);
        \end{scope}

    \end{tikzpicture}
    \caption{A pictorial representation of the entire model of the schedule for 7 skippers and 6 boats.
        The schedule is reproduced on the right. In the centre we have the 7 skippers, on left the
        $\modMatch$ and $\match$ arrays, and along the bottom the $\timeVar$
    array. The arrows signify channeling between parts of the model.}
    \label{schedChanges}
\end{figure}
\end{landscape}}
